The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-18 EducProposal.Rmd
Deleted unncessary files and edited proposal accordingly

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
date: "October 17, 2014"
author: "Sam Dundon and Thierry Racaud"
output: html_document
bibliography:
  - Main.bib
---
* * * 
```{r echo=FALSE,cache=TRUE}
# Install necessary packages
library(maps)
library(mapdata)
```

@@

```{r echo=FALSE,cache=TRUE}
map('worldHires', 'sweden', col="gray90", fill=TRUE)

map('worldHires',
    c('UK', 'Ireland', 'Isle of Man','Isle of Wight','Wales:Anglesey'),
    xlim=c(-11,3), ylim=c(49,60.9),
    col="gray90", fill=TRUE)

map('worldHires','France', xlim=c(-8.2,8.5), ylim=c(42.2,51.1),
    col="gray90", fill=TRUE)

@@

```{r, echo=FALSE, include=FALSE, cache=TRUE}
# Install rempis from Christpher Gandrud's website
devtools::install_github('christophergandrud/repmis')
library(repmis)
# Load citation package
pkgs <- c('dplyr','ggplot2')
repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')

>>>>

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
date: "October 17, 2014"
author: "Sam Dundon and Thierry Racaud"
output: html_document
bibliography:
  - Main.bib
---
* * * 
```{r echo=FALSE,cache=TRUE,include=FALSE}
# Set working directory
setwd('~/DataAnalysis/')

# Install necessary packages
# Install rempis from Christpher Gandrud's website
devtools::install_github('christophergandrud/repmis')
library(repmis)
# Load citation package
pkgs <- c('dplyr','ggplot2')
repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')

@@

@@
